Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-22 paper-v1.tex
Overall fixes (lost zSNARK reference)

From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.

@@

\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts (EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see § Privacy in 3.2).

\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}). In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback. Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, enabling a virtuous loop of verification. An interesting addition would be to introduce a rank of peer-reviews resulting from the community feedback via a voting process (see 4.1  Future developments). It's conceivable that the community members that engage in assessing the quality of peer-reviews could be incentivized as well. This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer-reviews would be also in the interest of the agents at play.

@@

\subsubsection{Privacy}
The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent and via private transactions allowed by AZTEC Protocol\cite{AZTEC}'s security layer.

@@

\small{
\subsubsection{Supplementary material}
Source code, DOI: 10.5281/zenodo.3971044; 
\newline DApp, https://ants-review.on.fleek.co;

>>>>

From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum-Wood}.

@@

\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts (EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).

\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}). In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback. Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, enabling a virtuous loop of verification. An interesting addition would be to introduce a rank of peer-reviews resulting from the community feedback via a voting process (see 4.1). It's conceivable that the community members that engage in assessing the quality of peer-reviews could be incentivized as well. This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer-reviews would be also in the interest of the agents at play.

@@

\subsubsection{Privacy}
The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent and via private transactions allowed by AZTEC Protocol \cite{AZTEC}'s security layer.

@@

\small{
\subsubsection{Supplementary material}
Source code, DOI: 10.5281/zenodo.3971044; 
\newline DApp: https://ants-review.on.fleek.co;
